---
title: "Spanish Regions and Aging in R"
author: "Aitor Alexander Gutierrez Valero"
date: '2022-08-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(readr)
library(dplyr)
library(ggplot2)
library(leaflet)
library(mapSpain)
```
### GDP per capita of Spanish Regions in the year 2000 and 2019
#### From the Instituto National de Estadística and the Instituto Geográfico Nacional. Euros Inflation Adjusted to 2019
##### First, I imported data relating to Spain's GDP per capita in 2000 and 2019, and from the "mapSpain" package I imported "pobmun19" which is a df  including Spain's 2019 census. Next, I cleaned up the GDP df in order to merge it with the census df.

```{r GDPpc_Spain, echo = FALSE, show_col_types = FALSE}
GDPpc_spain <- read_csv("GDP_Per_Capita_Spanish_Regions_2000_2019.csv",) #Import Spanish Provinces Data
GDPpc_spain["Province"][GDPpc_spain["Province"] == "Álava"] <- "Araba/Álava" #IF ALAVA, CHANGE TO ARABA/ALAVA
names(GDPpc_spain)[1]<-paste("provincia")
head(GDPpc_spain)

census <- mapSpain::pobmun19
head(census)

census_gdp <- merge(census,GDPpc_spain,by="provincia")
head(census_gdp)

codelist <- mapSpain::esp_codelist
```

```{r Testing, echo=FALSE}
# Spain <- GENERATES A GREY MAP OF SPAIN WITH SURROUNDING COUNTRIES
# leaflet() %>%
# setView(
# lat = 39.6566,
# lng = -3.7038400,
# zoom = 5.5
# ) %>%
# addProviderEspTiles(provider = "IGNBase.Gris")
# #addProviderEspTiles(provider = "RedTransporte.Carreteras")
# Spain

# census <- mapSpain::pobmun19
# 
# # Extract CCAA from base dataset
# 
# codelist <- mapSpain::esp_codelist
# 
# census <-
#   unique(merge(census, codelist[, c("cpro", "codauto")], all.x = TRUE))
# census
# 
# # Summarize by CCAA
# census_ccaa <-
#   aggregate(cbind(pob19, men, women) ~ codauto, data = census, sum)
# 
# census_ccaa$porc_women <- census_ccaa$women / census_ccaa$pob19
# census_ccaa$porc_women_lab <-
#   paste0(round(100 * census_ccaa$porc_women, 2), "%")
# census_ccaa
# 
# # Merge into spatial data
# 
# CCAA_sf <- esp_get_ccaa()
# CCAA_sf <- merge(CCAA_sf, census_ccaa)
# Can <- esp_get_can_box()
# 
# ggplot(CCAA_sf) +
#   geom_sf(aes(fill = porc_women),
#     color = "grey70",
#     lwd = .3
#   ) +
#   geom_sf(data = Can, color = "grey70") +
#   geom_sf_label(aes(label = porc_women_lab),
#     fill = "white", alpha = 0.5,
#     size = 3,
#     label.size = 0
#   ) +
#   scale_fill_gradientn(
#     colors = hcl.colors(10, "Blues", rev = TRUE),
#     n.breaks = 10,
#     labels = function(x) {
#       sprintf("%1.1f%%", 100 * x)
#     },
#     guide = guide_legend(title = "Porc. women")
#   ) +
#   theme_void() +
#   theme(legend.position = c(0.1, 0.6))
```

```{r 2000_GDPpc}

```

```{r 2019_GDPpc,}

```

```{r 2000_2019_GDPpc_%_Change}

```

```{r 2000_2019_GDPpc_Absolute_Change}

```

